Ice sheet mass flows

### 2024-07-30 sankey.tex
Ice shelf submarine freeze/melt separated into gross not net terms
Uses Paolo (2023) http://doi.org/10.5194/tc-17-3409-2023 rather than Davison (2023) http://doi.org/10.1126/sciadv.adi0186

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})}
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[xshift=15mm]f0.right}, anchor=right,
          forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \qq{f0}/f0i}}
    } {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[xshift=15mm]f0.right}, anchor=right,
          forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \Q{vML}/MLi, \qq{f0}/f0i}}
    }

@@

>>>>

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN}+\Q{vSUBF})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN}+\Q{vSUBF})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})}
      },
    }

@@

    \sankeynode{name=SUBF, quantity=\Q{vSUBF},
      at={[yshift=-\yoff]SF.south}, anchor=left}

    \ifthenelse{\Q{vMG} > \Q{vML}} {
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN}+\Q{vSUBF},
        at={[xshift=30mm, yshift=\yoff]SUBF.south}, anchor=right,
        forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vSUBF}/SUBFi}}
    } {
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN}+\Q{vSUBF},
        at={[xshift=30mm, yshift=\yoff]SUBF.south}, anchor=right,
        forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \Q{vML}/MLi, \qq{f0}/f0i, \Q{vSUBF}/SUBFi}}
    }

@@

    \ifnum \numexpr\Q{vSUBF} > 0
    \labelleft{SUBF}
    \sankeystart[water]{SUBF}
    \sankeydubins[water-to-ice]{SUBF}{SUBFi}
    \fi
